Seshadri constants of curve configurations on surfaces

### 2024-03-18 sc-curve-config.tex
Changes by Krishna-18 March (6:00PM)

\begin{example}
		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. 
		Then $X$ contains the following 48 lines; 
  %(denoted by $l_{\alpha, \beta}$); 
  16 from each of the following three types: 
		\begin{eqnarray*}
			A: \quad x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta x_3, \\
			A': \quad x_0 = \alpha x_2 \; \text{and} \; x_1 = \beta x_3, \\
			A'': \quad x_0 = \alpha x_3 \; \text{and} \; x_1 = \beta x_2,
		\end{eqnarray*}
		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity. We fix two enumerations $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.

@@

{\color{red} Can we remove the following paragraph?}

For the convenience of the reader, we quickly recall the argument below.  
		It suffices to verify this assertion for a line of type $A$. Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$. 
		In fact, these points are obtained by intersecting the lines in $\{l_{\alpha_i,\beta_j} \mid 1\leq j \leq 4 \} = X \cap V(x_0 - \alpha_i x_1)$ with those in  $\{l_{\alpha_i,\beta_j} \mid 1\leq i \leq 4 \} = X \cap V(x_2 - \beta_j x_3)$. 
		Note also that the sum of lines from any one of these sets is linearly equivalent to $\mathcal{O}_X(1)$. We also know that each line of type $A$ meets 
		4 lines each of type $A'$ and $A''$ and these points are all double points. Therefore in all there are 10 singular points on a line of type $A$. By a similar argument one can show this for lines of type $A'$ and type $A''$.

>>>>

\begin{example}
		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. 
		Then $X$ contains the following 48 lines; 
  %(denoted by $l_{\alpha, \beta}$); 
  16 from each of the following three types: 
		\begin{eqnarray*}
			A: \quad x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta x_3, \\
			A': \quad x_0 = \alpha x_2 \; \text{and} \; x_1 = \beta x_3, \\
			A'': \quad x_0 = \alpha x_3 \; \text{and} \; x_1 = \beta x_2,
		\end{eqnarray*}
		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity. %We fix two enumerations $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.

@@

For a fixed $\alpha \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$, the hyperplane section $X \cap V(x_0 - \alpha x_1)$ is the union of the four lines of type $A$ in $\mathcal{L}$ 
given by  
$x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta_j x_3$
for  $1\leq j \leq 4$. Consequiently, the sum of these four lines is linearly equivalent to $\mathcal{O}_X(1)$. The 48 lines in $\mathcal{L}$ can be partitioned into sets of 4 lines each such that the sum of the four lines in each set is 
linearly equivalent to $\mathcal{O}_X(1)$.

%{\color{red} Can we remove the following paragraph?}

%For the convenience of the reader, we quickly recall the argument %below.  
%		It suffices to verify this assertion for a line of type $A$. Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$. 
%		In fact, these points are obtained by intersecting the lines in $\{l_{\alpha_i,\beta_j} \mid 1\leq j \leq 4 \} = X \cap V(x_0 - \alpha_i x_1)$ with those in  $\{l_{\alpha_i,\beta_j} \mid 1\leq i \leq 4 \} = X \cap V(x_2 - \beta_j x_3)$. 
%		Note also that the sum of lines from any one of these sets is linearly equivalent to $\mathcal{O}_X(1)$. We also know that each line of type $A$ meets 
%		4 lines each of type $A'$ and $A''$ and these points are all double points. Therefore in all there are 10 singular points on a line of type $A$. By a similar argument one can show this for lines of type $A'$ and type $A''$.
